Continuous developmental change can explain discontinuities in word learning

### 2019-07-22 journal/ms.Rmd
journal version

Some researchers [e.g., @swingley2007; @yoshida2009; @pajak2016] proposed that the phonological form may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings. Rather, they may be encoding the phonological form of words in a probabilistic fashion. According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy representations.

@@

The main assumption of the model was that both word form and referent are encoded in a probabilistic fashion. The model provided a quantitative instantiation of the continuous development hypothesis [e.g., @swingley2007; @yoshida2009; @pajak2016]). More precisely, we showed that developmental changes in word-object mappings can be characterized as a continuous refinement in the precision of the probabilistic representations.

>>>>

Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that the phonological form may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings. Rather, they may be encoding the phonological form of words in a probabilistic fashion. According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy representations.

@@

The main assumption of the model was that both word form and referent are encoded in a probabilistic fashion. The model provided a quantitative instantiation of the continuous development hypothesis [@swingley2007; @yoshida2009; @pajak2016]. More precisely, we showed that developmental changes in word-object mappings can be characterized as a continuous refinement in the precision of the probabilistic representations.

### 2019-07-22 journal/ms.tex
journal version

Some researchers (Pajak et al., 2016; e.g., Swingley, 2007; Yoshida et
al., 2009) proposed that the phonological form may not be encoded in a
binary fashion, i.e., it is not the case that children either succeed or
fail in encoding minimal contrast when learning the meanings. Rather,
they may be encoding the phonological form of words in a probabilistic
fashion. According to this view, development does not so much involve a
qualitative shift (i.e., a sudden emergence of an ability that did not
exist before) as much as it consists in the continuous refinement of
initially noisy representations.

@@

The main assumption of the model was that both word form and referent
are encoded in a probabilistic fashion. The model provided a
quantitative instantiation of the continuous development hypothesis
(Pajak et al., 2016; e.g., Swingley, 2007; Yoshida et al., 2009)). More
precisely, we showed that developmental changes in word-object mappings
can be characterized as a continuous refinement in the precision of the
probabilistic representations.

>>>>

Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al.,
2009) proposed that the phonological form may not be encoded in a binary
fashion, i.e., it is not the case that children either succeed or fail
in encoding minimal contrast when learning the meanings. Rather, they
may be encoding the phonological form of words in a probabilistic
fashion. According to this view, development does not so much involve a
qualitative shift (i.e., a sudden emergence of an ability that did not
exist before) as much as it consists in the continuous refinement of
initially noisy representations.

@@

The main assumption of the model was that both word form and referent
are encoded in a probabilistic fashion. The model provided a
quantitative instantiation of the continuous development hypothesis
(Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009). More
precisely, we showed that developmental changes in word-object mappings
can be characterized as a continuous refinement in the precision of the
probabilistic representations.
